A flexible integer linear programming formulation for scheduling clinician on-call service in hospitals

### 2019-08-30 paper/paper.intro.tex
Add acks + funding sections
- Fix affiliation order, minor intro corrections
- TODO: add CPU specs to results section

Hospital departments provide services where patient needs, and thus the system's demands, often exceed the available supply. In particular, on-call schedules for a fixed number of health-care providers are central to the efficient running of hospitals. Carefully allocated schedules are meant to simultaneously ensure sufficient resources are provided to patients while not overworking clinicians to prevent costly mistakes [ref]. It is common practice for on-call schedules in hospitals to be created manually, yet manually-created schedules are prone to errors and potential for various biases [ref]. First, when there is a large number of clinicians in a single department, or the constraints that need to be satisfied by the department are very complex, a manual method may not provide an optimal schedule. Second, such methods are likely to overlook certain constraints that must be maintained to have an operational department, such as preventing many consecutive work blocks from being assigned or ensuring clinicians are allocated a specific amount of work blocks throughout the year. Third, manual scheduling is often time-consuming for the person developing the schedule. For these reasons, it is important to develop automated methods that can generate optimal schedules that satisfy the given constraints of the hospital department. \\
%For example, it is important that a hospital department allocates its resources, such as the availability of a finite number of clinicians, optimally, to ensure the best possible service for its patients.

>>>>

Hospital departments provide services where patient needs, and thus the system's demands, often exceed the available supply. In particular, on-call schedules for a fixed number of health-care providers are central to the efficient running of hospitals. Carefully allocated schedules are meant to simultaneously ensure sufficient resources are provided to patients while not overworking clinicians to prevent costly mistakes. It is common practice for on-call schedules in hospitals to be created manually, yet manually-created schedules are prone to errors and potential for various biases. First, when there is a large number of clinicians in a single department, or the constraints that need to be satisfied by the department are very complex, a manual method may not provide a schedule that satisfies all clinicians. Second, such methods are likely to overlook certain constraints that must be maintained to have an operational department, such as preventing many consecutive work blocks from being assigned or ensuring clinicians are allocated a specific amount of work blocks throughout the year. Third, manual scheduling is often time-consuming for the person developing the schedule. For these reasons, it is important to develop automated methods that can generate optimal schedules that satisfy the given constraints of the hospital department. \\
%For example, it is important that a hospital department allocates its resources, such as the availability of a finite number of clinicians, optimally, to ensure the best possible service for its patients.

### 2019-08-30 paper/paper.tex
SM edits affiliations
Add acks + funding sections
- Fix affiliation order, minor intro corrections
- TODO: add CPU specs to results section

\author[1, 5]{David Landsman}
\author[5]{Huiting Ma}
\author[5]{Jesse Knight}
\author[6]{Kevin Gough}
\author[2, 3, 4, 5]{Sharmistha Mishra}

\renewcommand\Affilfont{\itshape\small}
\affil[1]{Department of Computer Science, University of Toronto}
\affil[2]{Department of Medicine, Division of Infectious Disease, University of Toronto}
\affil[3]{Institute of Health Policy, Management and Evaluation, Dalla Lana School of Public Health, University of Toronto}
\affil[4]{Institute of Medical Sciences, University of Toronto}
\affil[5]{MAP Centre for Urban Health Solutions, Unity Health Toronto}
\affil[6]{Department of Medicine, St. Michael's Hospital}

@@

	\section{Introduction} \label{sec:introduction}
		\input{paper.intro.tex}
	\section{Problem} \label{sec:problem}
		\input{paper.problem.tex}
	\section{Methods} \label{sec:methods}
		\input{paper.methods.tex}
	\section{Results} \label{sec:results}
		\input{paper.results.tex}
	\section{Discussion} \label{sec:discussion}
		\input{paper.discussion.tex}
	\bibliographystyle{unsrt}
	\bibliography{references}
\end{document}

>>>>

\author[a, b]{David Landsman}
\author[a]{Huiting Ma}
\author[a]{Jesse Knight}
\author[c]{Kevin Gough}
\author[a, c, d, e]{Sharmistha Mishra}

\renewcommand\Affilfont{\itshape\small}
\affil[a]{MAP Centre for Urban Health Solutions, Unity Health Toronto, Toronto, ON, Canada}
\affil[b]{Department of Computer Science, University of Toronto, Toronto, ON, Canada}
\affil[c]{Department of Medicine, Division of Infectious Disease, St. Michael's Hospital, University of Toronto, Toronto, ON, Canada}
\affil[d]{Institute of Health Policy, Management and Evaluation, Dalla Lana School of Public Health, University of Toronto, Toronto, ON, Canada}
\affil[e]{Institute of Medical Sciences, University of Toronto, Toronto, ON, Canada}

@@

	\section{Introduction} \label{sec:introduction}
		\input{paper.intro.tex}
	\section{Problem} \label{sec:problem}
		\input{paper.problem.tex}
	\section{Methods} \label{sec:methods}
		\input{paper.methods.tex}
	\section{Results} \label{sec:results}
		\input{paper.results.tex}
	\section{Discussion} \label{sec:discussion}
		\input{paper.discussion.tex}
	\section{Acknowledgements} \label{sec:acknowledgements}
		\input{paper.acknowledgements.tex}
	\section{Funding} \label{sec:funding}
		\input{paper.funding.tex}

	\bibliographystyle{unsrt}
	\bibliography{references}
\end{document}
